Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-24 demystify.tex
updates

\begin{center}
  \includegraphics[scale=0.5]{files/emails.png}
\end{center}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to do it the \emph{right way}.

First, read the prof's website, see if they say something about contacting them. Many profs. explicitly indicate how prospective students should contact them (e.g., using specific email subjects). 
In general, the best way to catch the prof.'s attention is to \emph{customize your email} for them.  For example, read their papers, know what they work on, and see if you are interested in their research. Then send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email), you will not get a response.

@@

While I am not an international student, many of my students and collaborators are international.  I also mentor multiple students from Vietnam.  I also have various colleague and friends who were international students and have heard their stories.  I hope to capture their challenges and experiences in this document so that it can be useful for prospective international students.

>>>>

\begin{center}
  \includegraphics[scale=0.4]{files/emails.png}
\end{center}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to put effort into it and really do it the \emph{right way}.

First, read the prof's website, see if they say something about contacting them. Many profs. explicitly indicate how prospective students should (or should not) contact them (e.g., using specific email subjects).
In general, the best way to catch the prof.'s attention is to \emph{customize your email} for them.  For example, read their papers, know what they work on, and see if you are interested in their research. Then send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email or copy and paste paper titles), you will not get a response.

@@

While I am not an international student, many of my students and collaborators are.  I also mentor multiple students from Vietnan, and have various colleague and friends who were international students. I have heard their stories, and hope to capture their challenges and experiences in this document so that it can be useful for prospective international students.
